Projecting Global Filesystems into Local Containers for High-throughput Computing on HPC Resources

### 2019-01-23 paper.tex
Update paper build and add curated dir

\begin{figure}
\includegraphics[width=\linewidth]{plots/file-hist/alice-ocdb.pdf}
\caption{Distribution of file sizes in the \texttt{alice-ocdb.cern.ch} repo.
The vertical line at $2^{20}$~B marks a file size of 1~MB.}
\end{figure}

\begin{figure}
\includegraphics[width=\linewidth]{plots/file-hist/alice.pdf}
\caption{Distribution of file sizes in the \texttt{alice.cern.ch} repo.
The vertical line at $2^{20}$~B marks a file size of 1~MB.}
\end{figure}

\begin{figure}
\includegraphics[width=\linewidth]{plots/file-hist/atlas-condb.pdf}
\caption{Distribution of file sizes in the \texttt{atlas-condb.cern.ch} repo.
The vertical line at $2^{20}$~B marks a file size of 1~MB.}
\end{figure}

\begin{figure}
\includegraphics[width=\linewidth]{plots/file-hist/atlas.pdf}
\caption{Distribution of file sizes in the \texttt{atlas.cern.ch} repo.
The vertical line at $2^{20}$~B marks a file size of 1~MB.}
\end{figure}

\begin{figure}
\includegraphics[width=\linewidth]{plots/file-hist/boss.pdf}
\caption{Distribution of file sizes in the \texttt{boss.cern.ch} repo.
The vertical line at $2^{20}$~B marks a file size of 1~MB.}
\end{figure}

\begin{figure}
\includegraphics[width=\linewidth]{plots/file-hist/cms.pdf}
\caption{Distribution of file sizes in the \texttt{cms.cern.ch} repo.
The vertical line at $2^{20}$~B marks a file size of 1~MB.}
\end{figure}

\begin{figure}
\includegraphics[width=\linewidth]{plots/file-hist/cvmfs-config.pdf}
\caption{Distribution of file sizes in the \texttt{cvmfs-config.cern.ch} repo.
The vertical line at $2^{20}$~B marks a file size of 1~MB.}
\end{figure}

\begin{figure}
\includegraphics[width=\linewidth]{plots/file-hist/geant4.pdf}
\caption{Distribution of file sizes in the \texttt{geant4.cern.ch} repo.
The vertical line at $2^{20}$~B marks a file size of 1~MB.}
\end{figure}

\begin{figure}
\includegraphics[width=\linewidth]{plots/file-hist/grid.pdf}
\caption{Distribution of file sizes in the \texttt{grid.cern.ch} repo.
The vertical line at $2^{20}$~B marks a file size of 1~MB.}
\end{figure}

\begin{figure}
\includegraphics[width=\linewidth]{plots/file-hist/lhcb.pdf}
\caption{Distribution of file sizes in the \texttt{lhcb.cern.ch} repo.
The vertical line at $2^{20}$~B marks a file size of 1~MB.}
\end{figure}

\begin{figure}
\includegraphics[width=\linewidth]{plots/file-hist/na61.pdf}
\caption{Distribution of file sizes in the \texttt{na61.cern.ch} repo.
The vertical line at $2^{20}$~B marks a file size of 1~MB.}
\end{figure}

\begin{figure}
\includegraphics[width=\linewidth]{plots/file-hist/sft.pdf}
\caption{Distribution of file sizes in the \texttt{sft.cern.ch} repo.
The vertical line at $2^{20}$~B marks a file size of 1~MB.}
\end{figure}

>>>>

\begin{figure*}
\includegraphics[width=0.48\linewidth]{curated/sensitivity/container_efficiency_cache_percent_plt.pdf}
\includegraphics[width=0.48\linewidth]{curated/sensitivity/cache_efficiency_cache_percent_plt.pdf}
\includegraphics[width=0.48\linewidth]{curated/sensitivity/container_efficiency_request_percent_plt.pdf}
\includegraphics[width=0.48\linewidth]{curated/sensitivity/cache_efficiency_request_percent_plt.pdf}
\includegraphics[width=0.48\linewidth]{curated/sensitivity/container_efficiency_uses_percent_plt.pdf}
\includegraphics[width=0.48\linewidth]{curated/sensitivity/cache_efficiency_uses_percent_plt.pdf}
\caption{}
\end{figure*}
